Triptych: multiple inputs

### 2020-01-03 paper/multi.tex
Paper updates

\documentclass[draft]{article}
\usepackage[top=1.0in,bottom=1.0in,left=0.5in,right=0.5in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

@@

\subsection{Prover}
The prover algorithm accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1} \subset \G$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1} \subset \G$
\item a set of private keys $\{r^{(u)}\}_{u=0}^{w-1} \subset \F$
\item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F$
\item a set of linking tags $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$
\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \N$
\begin{itemize}
\item each $M_{l^{(u)}} = r^{(u)}G$ has its private key known to the prover
\item each $P_{l^{(u)}} = s^{(u)}G + a_uH$ has its amount and blinding factor known to the prover
\item each $J^{(u)} = (r^{(u)})^{-1}U$
\end{itemize}
\item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1} \subset \G$
\item a set of commitment amounts and blinding factors $\{(t_j,b_j)\}_{j=0}^{T-1} \subset \F$ such that:
\begin{itemize}
\item each $Q_j = t_jG + b_jH$ has its amount and blinding factor known to the prover
\item $\sum_{u=0}^{w-1} a_j - \sum_{j=0}^{T-1} b_j = 0$
\end{itemize}
\end{itemize}

@@

\subsection{Verifier}
The verifier accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1}$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1}$
\item a set of linking tags $\{J^{(u)}\}_{u=0}^{w-1}$
\item a proof generated by a prover
\end{itemize}

@@

%The decisional Diffie-Hellman assumption implies that the elements {Xj} and {Yj} are independent and uniformly distributed in a valid proof" should be changed to "The selection of random \rho values and the computation of each \mu_k and H(M_k) under the random oracle model imply that X, Y, and Z are statistically uniform and independent..." or something like that. DDH is a worse
The decisional Diffie-Hellman assumption implies that the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
The verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.

@@

\subsection{Special soundness}
We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm:
\begin{multline*}
\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, r, y \right) : r = \sum_{u=0}^{w-1} \hs(l^{(u)},M,P,Q)r^{(u)} \text{ and } \right. \\
\left. M_{l^{(u)}} = r_uG \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
\end{multline*}

% Since H is a random oracle, knowledge of r implies knowledge of {r^u} except with negligible probability
Collision resistance of $\hs$ means that, with high probability, knowledge of $r$ is equivalent to knowledge of $\{r^{(u)}\}$.
%  it's DL hardness on G together with the random oracle model
The combination of the discrete logarithm problem on $\G$ and the collision-resistance of $\hp$ allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
The binding property of Pedersen commitments ensures that, for properly constructed commitments, knowledge of $y$ implies that the sum of values of input commitments $\{P_{l^{(u)}}\}$ balances the sum of output commitments $\{Q_j\}$.
We may assume here that such commitments are correctly constructed, as this is shown by range proofs outside the scope of the proving system.

Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{x_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}x_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
Using the extracted values, compute
$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
for all $k \in [0,N)$.

@@

For each verification equation, we can therefore build a linear combination over $e$. For the $X$-check:
$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
The rightmost double sum of scalars is therefore, with high probability, equal to $r = \mu_{l^{(u)}} r^{(u)}$.

\textbf{OPEN QUESTION:} Does it necessarily follow that $\sum_{e=0}^m \theta_e {}_ez^{(u)}_R = \mu_{l^{(u)}} r^{(u)}$ for each $u$?

@@

Unfortunately, the same technique does not appear to apply for the $Y$-check. Doing so obtains the following:
$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
It is unclear how to associate this with the required witness extraction.

\textbf{OPEN QUESTION:} Does the witness extraction from the previous open question imply that each linking tag satisfies the required relation?

>>>>

\documentclass[draft]{article} % TODO: remove draft
\usepackage[top=1.0in,bottom=1.0in,left=0.5in,right=0.5in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

% TODO remove
\usepackage{lineno}
\linenumbers

@@

We now present a sigma protocol for the following relation:
\begin{multline*}
\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \right. \\
\left. M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
\end{multline*}

\subsection{Prover}
The prover algorithm accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1} \subset \G$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1} \subset \G$
\item a set of private keys $\{r^{(u)}\}_{u=0}^{w-1} \subset \F$
\item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F$
\item a set of linking tags $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$
\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \N$
\begin{itemize}
\item each $M_{l^{(u)}} = r^{(u)}G$ has its private key known to the prover
\item each $P_{l^{(u)}} = s^{(u)}G + a_uH$ has its amount and blinding factor known to the prover
\item each $J^{(u)} = (r^{(u)})^{-1}U$
\end{itemize}
\item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1} \subset \G$
\item a set of commitment amounts and blinding factors $\{(t_j,b_j)\}_{j=0}^{T-1} \subset \F$ such that:
\begin{itemize}
\item each $Q_j = t_jG + b_jH$ has its amount and blinding factor known to the prover
\item $\sum_{u=0}^{w-1} a_u - \sum_{j=0}^{T-1} b_j = 0$
\end{itemize}
\end{itemize}

@@

\subsection{Verifier}
The verifier accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1}$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1}$
\item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1}$
\item a set of linking tags $\{J^{(u)}\}_{u=0}^{w-1}$
\item a proof generated by a prover
\end{itemize}

@@

Under the random oracle model, the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
The verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.

@@

\subsection{Special soundness}
We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
\begin{multline*}
\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \right. \\
\left. \sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
\end{multline*}

Since aggregation coefficients are produced using a collision-resistant hash function modeling a random oracle and the discrete logarithm problem is assumed to be hard, the above sum requirements involving $\mu_k$ terms are sufficient to imply the desired witness requirements.
Further, this allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
The binding property of Pedersen commitments ensures that, for properly constructed commitments, knowledge of $y$ implies that the sum of values of input commitments $\{P_{l^{(u)}}\}$ balances the sum of output commitments $\{Q_j\}$.
We may assume here that such commitments are correctly constructed, as this is shown by range proofs outside the scope of the proving system.

Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{x_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$ (and the signing indices), and the Pedersen binding property ensures that (with high probability) we have:
$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}x_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
Using the extracted values, compute
$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
for all $k \in [0,N)$.

@@

For each verification equation, we can therefore build a linear combination over $e$. For the $X$-check:
$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
We therefore can define extractions for each $r^{(u)}$:
$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$

Observe that the same witnesses appear in the $Y$-check:
$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
This means the requirements on each $r^{(u)}$ are satisfied.

@@
